An Adolescent Mini-Neptune in the Kepler Field

### 2021-08-13 paper/ms.tex
update ms

\newcommand{\cn}{$\delta$~Lyr\ cluster} % cluster name
\newcommand{\sn}{Kepler\,1627} % star system name (binary)
\newcommand{\pn}{Kepler\,1627Ab} % planet name

@@

%TODO: might want to revise this text to better frame the boil-off phase...
%TODO: better citations on radius evolution?
For instance, the ``mini-Neptunes'', thought to be made of molten
rocky cores \citep{kite_atmosphere_2020} and extended atmospheric
envelopes of hydrogen and helium, are expected to shrink in size by
factors of several over their first $10^8$ years
\citep{owen_atmospheres_2016,owen_constraining_2020}.  Specifically,
they start with sizes of 4--12\,$R_\oplus$ near the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2--4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years of disk
dispersal \citep{owen_atmospheres_2016}, the combination of stellar
irradiation and internal heat may also power a more
gradual outflow, which can eventually deplete or entirely strip the
envelope from the rocky core
\citep{Owen_Wu_2013,ginzburg_corepowered_2018}.  Discovering young
planets, measuring their masses, and detecting their atmospheric
outflows are key steps toward testing this paradigm, which is often
invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017}.

@@

A previous clustering analysis of the Gaia data reported that
Kepler\,1627 (KIC 6184894; KOI 5245; TIC 120105470) is a member of the
\cn\ \citep{kounkel_untangling_2019}.  Given the statistical
validation of its close-in mini-Neptune
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we examined the age of the star and its putative host cluster more
closely (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is $35^{+6}_{-5}$\,Myr old, and that \sn\ is indeed a member
of the cluster.  Focusing on the planet itself
(Section~\ref{sec:planet}), we confirm through two independent
approaches that despite a previously unreported binary companion, it
is a mini-Neptune orbiting the G-dwarf primary star.  We conclude by
highlighting some broader implications for our ability to age-date a
statistical sample of planets (Section~\ref{sec:conc}).

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler and TESS views of the $\delta$\,Lyr cluster.} Colored
    points are kinematically selected members of the $\delta$\,Lyr
    cluster.  Both Kepler (gray squares) and TESS observed portions of
    the cluster.  Naked-eye stars ($m_{\rm V}<6.5$) are shown in gray;
    four of them (orange points) have their names annotated.
    Kepler\,1627 (green star) was observed during the entirety of the
    Kepler mission, and has been observed by TESS for two lunar months
    to date.  The colors of the other cluster members indicate the
    number of TESS sectors during which they have been observed.
    \label{fig:skychart}
	}
\end{figure}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f15c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is $35^{+6}_{-5}$\,Myr old.}  {\it Top:}
    Color-magnitude diagram of the \cn, IC\,2602 ($\approx35$\,Myr),
    the Pleiades ($\approx 115$\,Myr; \citealt{dahm_2015}), and the
    field (background contours).  The right panel provides a closer
    view of stars on the pre-main-sequence.  The \cn\ and IC\,2602 are
    approximately the same isochronal age.  {\it Bottom:} TESS and
    Kepler stellar rotation period versus dereddened Gaia color, with
    the Pleiades (115\,Myr) and Praesepe (650\,Myr) shown for
    reference \citep{rebull_rotation_2016a,douglas_poking_2017}.
    Kepler\,1627 is shown with a yellow star.
   \label{fig:age}
	}
\end{figure*}

To assess the age of the cluster and our star of interest, we used a
combination of the isochronal, gyrochronal, and lithium-based
age-dating.

@@

We meaured the isochrone age using an empirical approach.  The left
panel of Figure~\ref{fig:age} shows the color-magnitude diagram (CMD)
of stars in the \cn, IC\,2602, the Pleiades, and the field.  The stars
shown in the \cn\ are selected based on their positions and
kinematics, as discussed in Appendix~\ref{app:kinematicselection}.
Those from the Pleiades and IC\,2602 are adopted from
\citet{cantatgaudin_gaia_2018}, and the field stars are from the Gaia
EDR3 Catalog of Nearby Stars \citep{gaia_gcns_2021}.  We cleaned these
following identical data filtering criteria discussed in Appendix~B of
\citet{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  These filters were
designed to include genuine binaries while omitting instrumental
artifacts.  We then corrected for extinction by querying the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}},
and by then applying the extinction coefficients $k_X\equiv A_X/A_0$
computed by \citet{GaiaCollaboration2018} while assuming that $A_0 =
3.1 E(B-V)$.  For IC\,2602, the Pleaides, and the \cn, this procedure
yielded a respective mean and standard deviation for the reddening of
$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.  These
values agree reasonably well with previously reported values from the
literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,kounkel_untangling_2019,bossini_age_2019}.

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and are
therefore approximately the same age.  In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$-$16$\,Myr; \citealt{pecaut_star_2016}).  The
pre-main-sequence M dwarfs of the \cn\ were intermediate between these
latter two groups.  To turn this heuristic interpolation into an
age measurement with an uncertainty, we used the empirical procedure
developed by \citet{gagne_mutau_2020}.  In brief, we fitted the
pre-main-sequence loci of a set of reference clusters, and the locus
of the target \cn\ was then modeled as a piecewise linear combination
of these reference clusters.  For our reference clusters, we adopted
members of UCL, IC\,2602, and the Pleaides from
\citet{damiani_stellar_2019} and \cite{CantatGaudin2018a}
respectively.  We removed binaries by requiring $\texttt{RUWE}<1.3$,
$\texttt{radial\_velocity\_error}$ below the 80$^{\rm th}$ percentile
of each cluster's distribution, and by manually excluding stars that
were obvious photometric binaries in the CMD.  We then passed a moving
box average and standard deviation across the CMD in 0.10\,mag bins,
fitted a univariate spline to the binned values, and assembled a
piecewise grid of hybrid isochrones spanning the ages between UCL to
the Pleiades following Equations~6 and~7 from
\citet{gagne_mutau_2020}.

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades,
and a 16\,Myr age for UCL \citep{dahm_2015,pecaut_star_2016}.
The age of the IC\,2602 cluster however is the most important
ingredient, since it receives the most weight in the interpolation.
As noted by \citet{bouma_cluster_2020}, plausible ages for IC\,2602
span 30\,Myr to 46\,Myr, with slightly older ages being preferred by
the lithium-depletion-boundary (LDB) measurements and younger ages by
the main-sequence turn-off
\citep{stauffer_rotational_1997,dobbie_ic_2010,david_ages_2015,randich_gaiaeso_2018,bossini_age_2019}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse case of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
35\,Myr age as our reference, yielding an age for the \cn\ of
$35^{+6}_{-5}$\, Myr, though it should be understood based on the
systematic uncertainties that an age of up to $\approx50$\,Myr remains
plausible.  Detailed analyses of the LDB or main-sequence turn-off in
the \cn\ could help clarify the issue, but both are beyond our scope.

@@

Of the \noriginal\ candidate \cn\ members reported by
\citet{kounkel_untangling_2019}, TESS data were available for
\nwithtess\ stars.  \footnote{Kepler rotation periods were derived by
\citet{mcquillan_rotation_2014} for 56 stars; in these cases, we
adopted the Kepler rotation period.  } We extracted light curves from
the TESS images using the nearest pixel to each star, and regressed
them against systematics with the causal pixel model implemented in
the \texttt{unpopular} package \citep{hattorio_2021_cpm}.  We then
measured candidate rotation periods using a Lomb-Scargle periodogram
\citep{lomb_1976,scargle_studies_1982,astropy_2018}.  To enable cuts
on crowding, we queried the Gaia source catalog for stars within a
$21\farcs0$ radius of the target star (1 TESS pixel).  We recorded the
number of stars within the aperture with greater brightness than the
target star, and with brightness within 1.25 and 2.5 TESS magnitudes
of the target star.

@@

The lower panel of Figure~\ref{fig:age} shows the resulting
\nkindefaultcleaning\ stars.  The majority of these stars fall below
the ``slow sequence'' of the Pleiades, consistent with a
gyrochronological age for the \cn\ below 100\,Myr.  Approximately 10
stars appear as outliers above the ``slow sequence''.  Assuming that
they are all false positives ({\it i.e.}, field interlopers), the
rotation period detection fraction would be
\nrotgood/\nkinwithtessandcrowding$\approx \nfracprot\%$.

Binarity is known to be an important factor in the density of stars
falling underneath the ``slow sequence''
\citep{meibom_effect_2007,gillen_ngts_2020,bouma_2021_ngc2516}.
Appendix~\ref{app:rotationbinarity} discusses this topic, and finds
evidence for similar effects to those that have been previously
discussed in the literature.

@@

To summarize, the age of the \cn\ cluster based on the empirical
fitting procedure described in Section~\ref{sec:cmd} is
$35^{+6}_{-5}$\,Myr.  This procedure hinges on the age adopted for
IC\,2602, since it is the closest reference cluster in the
color-magnitude diagram.  Gyrochronologically, while most of the G and
K dwarfs in the \cn\ have not yet converged to a slow sequence, their
rotation distribution and that of the F dwarfs is consistent with the
same age.  The rotation periods of other 30\,Myr to 50\,Myr clusters
({\it e.g.}, IC\,2602 and Collinder 135) are indistinguishable
(S.~Douglas, priv{.}~comm{.}).  The most precise age for \sn\ and its
planet are therefore also $35^{+6}_{-5}$\, Myr, based on the star's
spatial, kinematic, and rotational connection to this larger ensemble,
and the assumption that the planet formed very quickly after the star.

Beyond the kinematic and rotational lines of evidence for the youth of
\sn, there is a final consistency check: the abundance of
Li\,\textsc{I} as inferred from the 6708\,\AA\ doublet.  The utility
of this element for age dating young stars has been reviewed by
\citet{soderblom_ages_2014}.  We acquired an iodine-free spectrum from
Keck/HIRES on the night of 26 March 2021 using the standard setup and
reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  Following the equivalent width measurement
procedure described by \citet{bouma_2021_ngc2516}, we measure ${\rm
EW}_{\rm Li} = 233^{+5}_{-7}\,$m\AA.   Note that this value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA\.  Given $T_{\rm
eff} \approx 5500\,{\rm K}$, this measurement is also in agreement
with an age for the star between 30\,Myr and 50\,Myr (see {\it e.g.},
Figure~9 of \citealt{bouma_2021_ngc2516}, or the data from
\citealt{randich_gaiaeso_2018}).

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f11.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit from transit timing variations.}
    The time of each transit was measured, along with the local slope
    of the light curve.  The two quantities appear anti-correlated,
    which is most easily explained by starspot crossings during the
    first (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa are most easily understood by considering
    that the flux from the star changes by $\sim$60\,ppt per half
    rotation period ($\sim$1.3\,days).
		\label{fig:ttvslope}
	}
\end{figure}

@@

If the \pn\ transit signal is created by a bonafide planet,  then to
our knowledge its age would make it the youngest planet yet found by
the main Kepler mission\footnote{The re-purposed K2 mission found two
slightly younger systems: K2-33b
\citep{David_et_al_2017,Mann_K2_33b_2016} and V1298 Tau
\citep{david_four_2019}}.  A portion of the light curve is shown with
the phase-folded transit in Figure~\ref{fig:lc}.  The dominant signal
in the \texttt{PDCSAP} photometry is a quasi-periodic starspot signal
with a peak-to-peak amplitude that varies between roughly 2\% and 8\%,
depending on the degree of asymmetry in spot coverage between the
stellar hemispheres.  The starspot signal repeats every
$2.642\pm0.042$\,days, where we have adopted an uncertainty based on
the scatter observed between different portions (quarters) of the
time-series data.  The details of how we model this starspot signal to
derive the parameters of the planet are discussed in
Appendix~\ref{app:gptransit}.  The results, given in
Table~\ref{tab:posterior}, are consistent with a mini-Neptune sized
planet ($3.56\pm 0.04\,R_\oplus$) on a circular 7.2\,day orbit
($e<0.XX$), around a G8V star ($0.91 \pm 0.05 R_\odot$).  {\bf TODO
quote the eccentricity limit}

Could the transit signal be produced by anything other than a planet
orbiting this near-solar analog?  \citet{morton_false_2016} considered
the false positive scenarios of a foreground eclipsing binary, a
hierarchical triple-star binary system, and a background eclipsing
binary.  Based on the transit shape, \citet{morton_false_2016} found
the latter scenario to be the only possible case, with a
(model-dependent) probability of $\approx10^{-5}$.  While this
statistical validation is reassuring, ``validated'' planets have been
shown to be false positives \citep{shporer_three_2017}.  Most
failures of the statistical validation approach arise when attempting
to separate the smallest stars from identically-sized gas giant
planets.  With a size of $\approx 3.6\,R_\oplus$, Kepler\,1627b does
not meet this concern.  The fact that we detect a low-mass stellar
companion in archival Keck-NIRC2 Kp-band (2.12\,$\mu $m) imaging does
not change the conclusion: the companion star contributes 1\% of the
flux observed by Kepler.  Combined with the observed transit depth and
shape (Appendix~\ref{app:companionstar}), a planet transiting the
primary star is the only plausible interpretation of the
data.

{\bf todo: LGB to check numbers on full-dataset transit ecc and b} 
Two additional new lines of evidence confirm the planetary
interpretation.  First, the $\approx$100 days of 1-minute
cadenced Kepler observations reduce the cadence-induced smearing,
enabling a more precise measurement of the transit impact parameter
\citep{kipping_binning_2010}.  The planet transits with $b<0.YY$
(3-$\sigma$) from the 1-minute cadenced data, compared to $<0.XX$
(3-$\sigma$) from the 30-minute data.

{\bf todo: Kento to check numbers on per-transit analysis} 
The second line of evidence comes from our transit timing analysis. We
isolated each of the 144 observed transits to within $\pm4.5$\,hr of
each transit, and fitted each window with both {\it i)} a local
second-order polynomial and transit, and {\it ii)} a local linear
trend.  We let the mid-time of each transit float, and then calculated
the residual between the measured mid-time and that of a perfectly
periodic orbit.  This residual, the ``transit timing variation''
(TTV), is plotted in Figure~\ref{fig:ttvslope} against the local
linear slope.  Only a handful of Kepler Objects of Interest have shown
this correlation \citep{holczer_time_2015}, which is most readily
interpreted as a TTV induced by unresolved starspot crossings
\citep{mazeh_time_2015}.  This is of course only possible if the
planet is transiting the primary star, which excludes the any of the
aforementioned false positive scenarios.  It also implies that the
planet's orbit is prograde.  The latter interpretation assumes that
the dominant photometric variability is induced by dark spots, rather
than bright faculae.  Given the observed transition of Sun-like
stellar variability from spot to faculae-dominated regimes, we expect
this inference to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

>>>>

\newcommand{\cn}{$\delta$\ Lyr\ cluster} % cluster name
\newcommand{\sn}{Kepler\,1627} % star system name (binary)
\newcommand{\pn}{Kepler\,1627Ab} % planet name

@@

%TODO: might want to revise this text to better frame the boil-off phase...
%TODO: better citations on radius evolution?
For instance, the ``mini-Neptunes'', thought to be made of molten
rocky cores \citep{kite_atmosphere_2020} and extended atmospheric
envelopes of hydrogen and helium, are expected to shrink in size by
factors of several over their first $10^8$ years
\citep{owen_atmospheres_2016,owen_constraining_2020}.  Specifically,
they start with sizes of 4--12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2--4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years of the disk's pressure
support being removed \citep{owen_atmospheres_2016}, the combination of stellar
irradiation and internal heat may also power a more
gradual outflow which can eventually deplete or entirely strip the
envelope from the rocky core
\citep{Owen_Wu_2013,ginzburg_corepowered_2018}.  Discovering young
planets, measuring their masses, and detecting their atmospheric
outflows are key steps toward testing this paradigm, which is often
invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017}.

@@

A previous clustering analysis of the Gaia data reported that
Kepler\,1627 (KIC 6184894; KOI 5245; TIC 120105470) is a member of the
\cn\ \citep{kounkel_untangling_2019}.  Given the previous statistical
validation the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we examined the age of the star and its putative host cluster more
closely (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is $35^{+6}_{-5}$\,Myr old, and that \sn\ is indeed a member
of the cluster.  Focusing on the planet itself,
we confirm that despite the presence of a previously unreported binary companion,
the planet orbits the G-dwarf primary star on an orbit that appears aligned
with the stellar rotation axis
(Section~\ref{sec:planet}).  We conclude by
highlighting broader implications for our ability to age-date a
statistical sample of planets (Section~\ref{sec:conc}).

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler and TESS views of the $\delta$\,Lyr cluster.} Colored
    points are kinematically selected members of the $\delta$\,Lyr
    cluster.  Both Kepler (gray squares) and TESS observed portions of
    the cluster.  Naked-eye stars ($m_{\rm V}<6.5$) are shown in gray;
    four of them (orange circles) have their names annotated.
    Kepler\,1627 (green star) was observed during the entirety of the
    Kepler mission, and has been observed by TESS for two lunar months
    to date.  The colors of the other cluster members indicate the
    number of TESS sectors during which they have been observed.
    \label{fig:skychart}
	}
\end{figure}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f15c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is $35^{+6}_{-5}$\,Myr old.}  {\it Top:}
    Color-magnitude diagram of the \cn, IC\,2602 ($\approx35$\,Myr),
    the Pleiades ($\approx 115$\,Myr; \citealt{dahm_2015}), and the
    field (gray).  The right panel provides a zoomed
    view of stars on the pre-main-sequence.  The \cn\ and IC\,2602 are
    approximately the same isochronal age.  {\it Bottom:} TESS and
    Kepler stellar rotation periods versus dereddened Gaia colors, with
    the Pleiades and Praesepe (650\,Myr) shown for
    reference \citep{rebull_rotation_2016a,douglas_poking_2017}.
    The \cn\ is gyrochronally younger than the Pleiades.
   \label{fig:age}
	}
\end{figure*}

To assess the age of the cluster and our star of interest, we used a
combination of isochronal, gyrochronal, and lithium-based
age-dating.

@@

We meaured the isochrone age using an empirical approach.  The left
panel of Figure~\ref{fig:age} shows the color-magnitude diagram (CMD)
of stars in the \cn, IC\,2602, the Pleiades, and the field.  The stars
shown in the \cn\ are selected based on their positions and
kinematics, as discussed in Appendix~\ref{app:kinematicselection}.
Those from the Pleiades and IC\,2602 are adopted from
\citet{cantatgaudin_gaia_2018}, and the field stars are from the Gaia
EDR3 Catalog of Nearby Stars \citep{gaia_gcns_2021}.  We cleaned these
following identical data filtering criteria discussed in Appendix~B of
\citet{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  These filters were
designed to include genuine binaries while omitting instrumental
artifacts.  We then corrected for extinction by querying the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}},
and by then applying the extinction coefficients $k_X\equiv A_X/A_0$
computed by \citet{GaiaCollaboration2018} while assuming that $A_0 =
3.1 E(B-V)$.  For IC\,2602, the Pleiades, and the \cn, this procedure
yielded a respective mean and standard deviation for the reddening of
$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.  These
values agree reasonably well with previously reported values from the
literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,kounkel_untangling_2019,bossini_age_2019}.

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and are
therefore approximately the same age.  In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).  The
pre-main-sequence M dwarfs of the \cn\ were intermediate between these
latter two groups.  To turn this heuristic interpolation into an
age measurement, we used the empirical procedure
developed by \citet{gagne_mutau_2020}.  In brief, we fitted the
pre-main-sequence loci of a set of reference clusters, and the locus
of the target \cn\ was then modeled as a piecewise linear combination
of these reference clusters.  For our reference clusters, we adopted
members of UCL, IC\,2602, and the Pleiades from
\citet{damiani_stellar_2019} and \cite{CantatGaudin2018a}
respectively.  We removed binaries by requiring $\texttt{RUWE}<1.3$,
$\texttt{radial\_velocity\_error}$ below the 80$^{\rm th}$ percentile
of each cluster's distribution, and by manually excluding stars that
were obvious photometric binaries in the CMD.  We then passed a moving
box average and standard deviation across the CMD in 0.10\,mag bins,
fitted a univariate spline to the binned values, and assembled a
piecewise grid of hybrid isochrones spanning the ages between UCL to
the Pleiades following Equations~6 and~7 from
\citet{gagne_mutau_2020}.

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades,
and a 16\,Myr age for UCL \citep{dahm_2015,pecaut_star_2016}.
The age of IC\,2602 however is the most important
ingredient, since it receives the most weight in the interpolation.
Plausible ages for IC\,2602
span 30\,Myr to 46\,Myr, with slightly older ages being preferred by
the lithium-depletion-boundary (LDB) measurements and younger ages by
the main-sequence turn-off
\citep{stauffer_rotational_1997,dobbie_ic_2010,david_ages_2015,randich_gaiaeso_2018,bossini_age_2019,bouma_cluster_2020}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse case of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
35\,Myr age as our reference, yielding an age for the \cn\ of
$35^{+6}_{-5}$\, Myr, though it should be understood based on the
systematic uncertainties that an age of up to $\approx50$\,Myr remains
plausible.  Detailed analyses of the LDB or main-sequence turn-off in
the \cn\ could help resolve the issue, but both are beyond our scope.

@@

Of the \noriginal\ candidate \cn\ members reported by
\citet{kounkel_untangling_2019}, TESS data were available for
\nwithtess\ stars.\footnote{Kepler rotation periods were derived by
\citet{mcquillan_rotation_2014} for 56 stars; in these cases, we
adopted the Kepler rotation period.  } We extracted light curves from
the TESS images using the nearest pixel to each star, and regressed
them against systematics with the causal pixel model implemented in
the \texttt{unpopular} package \citep{hattorio_2021_cpm}.  We then
measured candidate rotation periods using a Lomb-Scargle periodogram
\citep{lomb_1976,scargle_studies_1982,astropy_2018}.  To enable cuts
on crowding, we queried the Gaia source catalog for stars within a
$21\farcs0$ radius of the target star (1 TESS pixel).  We recorded the
number of stars within the aperture with greater brightness than the
target star, and with brightness within 1.25 and 2.5 TESS magnitudes
of the target star.

@@

The lower panel of Figure~\ref{fig:age} shows the resulting
\nkindefaultcleaning\ stars.  The majority of these stars fall below
the ``slow sequence'' of the Pleiades, consistent with a
gyrochronological age for the \cn\ below 100\,Myr.  Approximately 10
stars appear as outliers above the ``slow sequence''.  Assuming that
they are all false positives ({\it i.e.}, field interlopers), the
rotation period detection fraction would be
$\nrotgood/\nkinwithtessandcrowding \approx \nfracprot\%$.

Binarity is known to be an important factor in the density of stars
falling underneath the slow sequence
\citep{meibom_effect_2007,gillen_ngts_2020,bouma_2021_ngc2516}.
Appendix~\ref{app:rotationbinarity} discusses this topic, and finds
evidence for similar effects to those that have been previously
discussed in the literature.

@@

In brief , the age of the \cn\ cluster based on the empirical
fitting procedure described in Section~\ref{sec:cmd} is
$35^{+6}_{-5}$\,Myr.  This procedure hinges on the age adopted for
IC\,2602, since it is the closest reference cluster in the
color-magnitude diagram.  Gyrochronologically, while most of the G and
K dwarfs in the \cn\ have not yet converged to a slow sequence, their
rotation distribution and that of the F dwarfs is consistent with the
same age.  The rotation periods of other 30\,Myr to 50\,Myr clusters
({\it e.g.}, IC\,2602 and IC\,2391) are indistinguishable
\citep{douglas_stephanie_t_2021_5131306}.  The most precise age for \sn\ and its
planet are therefore also $35^{+6}_{-5}$\, Myr, based on the star's
spatial, kinematic, and rotational connection to this larger ensemble,
and the assumption that the planet formed very quickly after the star.

%TODO:  check Teff here once you have it.
Beyond the kinematic and rotational lines of evidence for the youth of
\sn, there is a final consistency check: the abundance of
Li\,\textsc{I} as inferred from the 6708\,\AA\ doublet.  The utility
of this element for age dating young stars has been reviewed by
\citet{soderblom_ages_2014}.  We acquired an iodine-free spectrum from
Keck/HIRES on the night of 26 March 2021 using the standard setup and
reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  Following the equivalent width measurement
procedure described by \citet{bouma_2021_ngc2516}, we measure ${\rm
EW}_{\rm Li} = 233^{+5}_{-7}\,$m\AA.   Note that this value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Given $T_{\rm
eff} \approx 5500\,{\rm K}$, this measurement is also in agreement
with an age for the star between 30\,Myr and 50\,Myr (see {\it e.g.},
Figure~9 of \citealt{bouma_2021_ngc2516}, or the data from
\citealt{randich_gaiaeso_2018}).

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f11.pdf}
		}

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f16.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
    {\it Top:} 
    The time of each Kepler transit was measured, along with the local slope
    of the light curve.  The two quantities appear anti-correlated,
    which is most easily explained by starspot crossings during the
    first (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa are most easily understood by considering
    that the flux from the star changes by $\sim$60\,ppt per half
    rotation period ($\sim$1.3\,days).
        {\it Bottom:} A Keck/HIRES transit was observed on 7 Aug 2021 UT,
    simultaneous with MUSCAT3.  A quadratic baseline trend was allowed
    in the fit.
    The resulting best-fit sky-projected obliquity is listed in red.
    \label{fig:obliquity}
	}
\end{figure}

@@

%TODO: fix sizes and numbers
If the \pn\ transit signal is created by a bonafide planet,  then to
our knowledge its age would make it the youngest planet yet found by
the main Kepler mission.\footnote{The re-purposed K2 mission found two
slightly younger systems: K2-33b
\citep{David_et_al_2017,Mann_K2_33b_2016} and V1298 Tau
\citep{david_four_2019}}  A portion of the light curve is shown with
the phase-folded transit in Figure~\ref{fig:lc}.  The dominant signal
in the \texttt{PDCSAP} photometry is a quasi-periodic starspot signal
with a peak-to-peak amplitude that varies between roughly 2\% and 8\%,
depending on the degree of asymmetry in spot coverage between the
stellar hemispheres.  The starspot signal repeats every
$2.642\pm0.042$\,days, where we have adopted an uncertainty based on
the scatter observed between different portions (quarters) of the
time-series data.  The details of how we model this starspot signal to
derive the parameters of the planet are discussed in
Appendix~\ref{app:gptransit}.  The results, given in
Table~\ref{tab:posterior}, are consistent with a mini-Neptune sized
planet ($3.56\pm 0.04\,R_\oplus$) on a circular 7.2\,day orbit
($e<0.XX$), around a G8V star ($0.91 \pm 0.05 R_\odot$).  {\bf TODO
quote the eccentricity limit}

Could the transit signal be produced by anything other than a planet
orbiting this near-solar analog?  \citet{morton_false_2016} considered
the false positive scenarios of a foreground eclipsing binary, a
hierarchical triple-star binary system, and a background eclipsing
binary.  Based on the transit shape, \citet{morton_false_2016} found
the latter scenario to be the only possible case, with a
(model-dependent) probability of $\approx10^{-5}$. Most
reported failures of the statistical validation approach have arisen when attempting
to separate the smallest stars from identically-sized gas giant
planets \citep[{\it e.g.},][]{shporer_three_2017}.  With a size of $\approx 3.5\,R_\oplus$, Kepler\,1627b does
not meet this concern.  The fact that we detect a low-mass stellar
companion in archival Keck-NIRC2 Kp-band (2.12\,$\mu $m) imaging does
not change the conclusion: the companion star contributes 1\% of the
flux observed by Kepler.  Combined with the observed transit depth and
shape (Appendix~\ref{app:companionstar}), a planet transiting the
primary star is the only plausible interpretation of the
data.

{\bf todo: LGB to check numbers on full-dataset transit ecc and b} 
Three additional new lines of evidence confirm the planetary
interpretation.  First, the $\approx$100 days of 1-minute
cadenced Kepler observations reduce the cadence-induced smearing,
enabling a more precise measurement of the transit impact parameter
\citep{kipping_binning_2010}.  The planet transits with $b<0.YY$
(3-$\sigma$) from the 1-minute cadenced data, compared to $<0.XX$
(3-$\sigma$) from the 30-minute data.

{\bf todo: Kento to check numbers on per-transit analysis} 
The second line of evidence comes from our transit timing analysis. We
isolated each of the 144 observed transits to within $\pm4.5$\,hr of
each transit, and fitted each window with both {\it i)} a local
second-order polynomial and transit, and {\it ii)} a local linear
trend.  We let the mid-time of each transit float, and then calculated
the residual between the measured mid-time and that of a perfectly
periodic orbit.  This residual, the ``transit timing variation''
(TTV), is plotted in Figure~\ref{fig:obliquity} against the local
linear slope.  Only a handful of Kepler Objects of Interest have shown
this correlation \citep{holczer_time_2015}, which is most readily
interpreted as a TTV induced by unresolved starspot crossings
\citep{mazeh_time_2015}.  This is only possible if the
planet transits the primary star, which excludes the
aforementioned false positive scenarios.  It also implies that the
planet's orbit is prograde.  The latter interpretation assumes that
the dominant photometric variability is induced by dark spots, rather
than bright faculae.  Given the observed transition of Sun-like
stellar variability from spot to faculae-dominated regimes, we expect
this inference to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

The final line of evidence confirming \pn\ comes from a spectroscopic
transit we measured from Keck/HIRES during the night of 7 Aug 2021
(UT) using the iodine cell for the wavelength calibration.  We
scheduled the transit using the ephemeris of
\citet{holczer_transit_2016}, which we verified using the available
TESS data.  We also acquired simultaneous multi-band photometry using
MUSCAT3, to help interpret the radial velocities \citep{Narita_2020}.
The lower panels in Figure~\ref{fig:obliquity} show the results.  The
photometry shows the expected starspot trend, along with the transit
and a likely starspot crossing event at ${\rm JD} - 2459433 = 0.955$.
The spectroscopic data show significant scatter, though a significant
increase in radial velocity is seen shortly after the expected
ingress.  We fitted the RVs using the \citet{hirano_analytic_2010} and
\citet{hirano_2011} models for the Rossiter-McLaughlin effect, and
considered the cases of a linear and quadratic trend.
% TODO finish this paragraph
We found $\chi^2_{\rm red} = X.XX$ for the best-fitting linear case, 
and
$\chi^2_{\rm red} = X.XX$ for the best-fitting quadratic, with a
$\Delta {\rm BIC} = Y.YY$ between the two, providing {\bf (very)
strong} evidence to prefer the latter.
